---
title: "Tufte Handout of Rmarkdown"
author: "Faryal Usman"
date: "`r Sys.Date()`"
output:
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  html_document:
    df_print: paged
link-citations: yes
subtitle: An implementation in R Markdown
bibliography: /Users/faru/Desktop/Tufte-implementation-of-Markdown/mybib2.bib
---


# Initial setup 
```{r setup, include = TRUE, warning=FALSE, echo = TRUE, message=FALSE} 
# Knitr options include:
  # include = TRUE
  # warning = FALSE
  # echo = TRUE
  # message = FALSE 
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk("/Users/faru/Desktop/Tufte-implementation-of-Markdown/external_file_chunk.r")
source("/Users/faru/Desktop/Tufte-implementation-of-Markdown/external_file_chunk.r")
```


# Loading relevant libraries 
```{r, warning = FALSE, echo = FALSE, message = FALSE, include = TRUE, echo = TRUE}
library(tufte)
library(tidyverse)
library(ggplot2)
library(bookdown)
```

# A plot of starwars data 
```{r, starwars-plot, fig.cap = 'A ggplot of starwars data', warning = FALSE}
starwars %>% 
  filter(species == "Human") %>% 
ggplot() +
  aes(x = eye_color, 
      y = height, color = eye_color) +
  geom_point() + ggtitle("Heights of humans by eye color in the Star Wars universe") + 
  theme(plot.title = element_text(size = 8, face = "bold"))
```





# A table of star wars data 
```{r, starwars-table}
starwars %>% 
  filter(species == "Human")  %>% 
  select(name, 
         height, 
         eye_color) %>% 
  knitr::kable(caption = "A knitr kable table of starwars humans eye color ")
```


# Code from an external source 
```{r, code-from-external-source}
# Finding the cube of some number through an external chunk 
y <- cube_function(5)
y

# Finding the square of some number through an external chunk 
x <- square_function(3)
x
```




# Cached code 
```{r time-consuming-function, cache = TRUE}

exponential_func <- function(reps) {
  result_list <- c(rep(NA,reps))
  for (i in 1:reps){
    if (i %% 2 == 0) {
      result_list[i] <- square_function(i)
    } else {
      result_list[i] <- cube_function(i)
    }
  }
  q <- max(result_list)
}
```





```{r eval-time-of-cached-function, dependson="time-consuming-function"}
start.time <- Sys.time()
first <- exponential_func(1e4)
first
end.time <- Sys.time()
time_taken = end.time - start.time 
time_taken
```



# Citations
In @xie2017dynamic, a book written by one of the authors of knitr, the author explores the applications of R to scientific discpline such as epidemiology, finance, biology and the social sciences as well as the variety of models that can be used.

In @xie2013knitr, the same author explores some of the more technical functionalities of knitr.
